### 2015-02-16 introduction.tex
Adding refs to optimal lattice stuff in 2d.

\label{sec:intro}
Reconstructing a solid model from a scattered set of points is a common and well studied problem in computer graphics. Interest in this problem is rooted in the desire to convert real life data-sets -- acquired from range and now increasingly from commodity hardware like the Kinect -- to 3D polygonal models. The idea also has a applications in model re-meshing and hole filling. \ednote{This needs more meat, it's a pretty weak ending to the intro paragraph.}

@@

  \mbox{} \hfill
	\includegraphics[width=.3\linewidth]{figures/lattice/cc_cell}
	\includegraphics[width=.3\linewidth]{figures/lattice/bcc_cell}
	\includegraphics[width=.3\linewidth]{figures/lattice/fcc_cell} \\
   \hfill \mbox{}
  \caption{\label{fig:lattices}%
  Sampling lattices (top) with with their corresponding Voronoi regions (bottom). Left to right are the CC, BCC and FCC lattices respectively.
  }
\end{figure*}

@@

Additionally, we consider the possibility of approximating the smoothed gradient field representation within function spaces that are
spanned by shifted versions of a single generating kernel. In the context of gradient estimation, introducing a shift in the direction
of the derivative has shown to improve overall gradient approximation fidelity in terms of gradient orientation and magnitude,
as well as displaying the ability to capture higher frequency details that are smoothed out in non-shifted schemes~\cite{gradrev}. Since the divergence operator is intimately connected to the gradient operator, these results are of interest to us. Using an appropriate discretization of the derivative/divergence operator is an important step in recovering the indicator function of the initial model. \ednote{Need to emphasize the error-kern here}

@@

\ednote{OVERALL: What is lacking from this intro is the true purpose of this work (from the surface reconstruction aspect.) We want to show that the BCC beats the CC lattice. NOT that our scheme is better than Kazhdan's. We do show this, but we need to emphasize it above!}

>>>>

\label{sec:intro}
Reconstructing a solid model from a scattered set of points is a common and well studied problem in computer graphics. Interest in this problem is rooted in the desire to convert real life data-sets -- data acquired from range scanners and now increasingly from commodity hardware like the Kinect -- to 3D polygonal models. The idea also has a applications in model re-meshing and mesh hole filling, when one has a poorly formatted mesh and would like a better representation of it.

@@

  \mbox{} \hfill
	\includegraphics[width=.3\linewidth]{figures/lattice/cc_cell}
	\includegraphics[width=.3\linewidth]{figures/lattice/bcc_cell}
	\includegraphics[width=.3\linewidth]{figures/lattice/fcc_cell} \\
   \hfill \mbox{}
  \caption{\label{fig:lattices}
  Sampling lattices (top) with with their corresponding Voronoi regions (bottom). Left to right are the CC, BCC and FCC lattices respectively.
  }
\end{figure*}

@@

Additionally, we consider the possibility of approximating the smoothed gradient field representation within function spaces that are
spanned by shifted versions of a single generating kernel. In the context of gradient estimation, introducing a shift in the direction
of the derivative has shown to improve overall gradient approximation fidelity in terms of gradient orientation and magnitude,
as well as displaying the ability to capture higher frequency details that are smoothed out in non-shifted schemes~\cite{gradrev}. Since the divergence operator is intimately connected to the gradient operator, these results are of interest to us. Using an appropriate discretization of the derivative/divergence operator is an important step in recovering the indicator function of the initial model. We also derive specific error bounds, based on an error kernel formulation, for approximations of linear operators in arbitrary shift invariant spaces.

@@

### 2015-02-16 relatedwork.tex
Adding refs to optimal lattice stuff in 2d.

Our approach aims to solve the Poisson surface reconstruction problem
in the setting of shift-invariant spaces. A crucial step in this
regard is the accurate estimation of the divergence of the gradient
field from the oriented point-set. Radial basis functions (RBFs) are
generally used in the context of the reconstruction of scattered data, 
however, RBF techniques are often computationally
expensive, requiring the solution of large unstable systems of
equations (for exact interpolation.) A proposed solution to this
problem is to ``\emph{re-sample}'' the input data onto a regular
shift-invariant space. This allows one to use efficient compact
reconstruction kernels and data processing techniques
\cite{variational,onvari}. Recently, an extension of this idea to box
spline spaces \cite{xu2012rec} proposes a variational reconstruction
framework in which the BCC lattice consistently outperforms the
Cartesian lattice. Our method takes a similar variational approach and
seeks to construct a smoothed lattice-based approximation of the
gradient of the indicator function (\SC{sec:obtainingV}). Our employed
constraints force the gradient to be close to zero away from the
surface, while maintaining a certain degree of smoothness in the
resulting approximation. This is preferable in comparison to other
works \cite{fftk,Kazhdan06,screenedk} in which each sample is
trilinearly distributed about either a grid or an oct-tree
respectively, and is known to over-smooth data.

>>>>

Outside of the context of surface reconstruction there has been considerable
evidence that shows non-Cartesian approaches to volume rendering 
\cite{firstbox, practicalbox, hvolrecon} and fluid flow \cite{lboltzman} outperform 
Cartesian approaches in both speed and memory consumption. Additionally, 
finite difference Laplacian stencils on non-Cartesian grids lead to reduced 
numerical dispersion compared to their Cartesian  counterparts (see e.g. 
\cite{hamilton2013, hamilton2013hexagonal} and references therein). It is 
therefore natural to question whether these advantages can be exploited 
within the context of surface reconstruction.

Our approach aims to solve the Poisson surface reconstruction problem
in the setting of general shift-invariant spaces. A crucial step in this
regard is the accurate estimation of the divergence of the gradient
field from the oriented point-set. Radial basis functions (RBFs) are
generally used in the context of the reconstruction of scattered data, 
however, RBF techniques are often computationally
expensive, requiring the solution of large unstable systems of
equations (for exact interpolation.) A proposed solution to this
problem is to ``\emph{re-sample}'' the input data onto a regular
shift-invariant space. This allows one to use efficient compact
reconstruction kernels and data processing techniques
\cite{variational,onvari}. Recently, an extension of this idea to box
spline spaces \cite{xu2012rec} proposes a variational reconstruction
framework in which the BCC lattice consistently outperforms the
Cartesian lattice. Our method takes a similar variational approach and
seeks to construct a smoothed lattice-based approximation of the
gradient of the indicator function (\SC{sec:obtainingV}). Our employed
constraints force the gradient to be close to zero away from the
surface, while maintaining a certain degree of smoothness in the
resulting approximation. This is preferable in comparison to other
works \cite{fftk,Kazhdan06,screenedk} in which each sample is
trilinearly distributed about either a grid or an oct-tree
respectively, and is known to over-smooth data.
